\documentclass[11pt, letterpaper]{article}

% --- PACKAGES ---
% Reduced margins to half an inch to maximize space while remaining printer-safe
\usepackage[left=0.5in,top=0.5in,right=0.5in,bottom=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{fontawesome5} % For contact icons
\usepackage{xcolor}

% --- COLORS & FORMATTING ---
\definecolor{darkblue}{RGB}{26, 64, 115} % ALDI-inspired professional blue

% Format section headers - reduced vertical spacing above and below the blue lines
\titleformat{\section}{\Large\bfseries\color{darkblue}}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{8pt}{4pt}

% Remove page numbers
\pagestyle{empty}

\begin{document}

% --- HEADER ---
\begin{center}
    {\Huge \textbf{\color{darkblue} PRESTON JENKINS}} \\ \vspace{4pt}
    \small 
    \faMapMarker \ 124 E Main St., Norman, OK 73069 \quad 
    \faPhone \ (405) 886-5038 \quad 
    \faEnvelope \ \href{mailto:preston.b.jenkins@gmail.com}{preston.b.jenkins@gmail.com}
\end{center}

\vspace{2pt}

% --- PROFESSIONAL SUMMARY ---
\section*{PROFESSIONAL SUMMARY}
Dependable and hardworking professional with 7 years of experience in client service and office operations, looking to transition into a physically active, hands-on retail role. Known for being a quick learner, keeping a cool head under pressure, and always showing up on time. Eager to bring my strong customer service skills, early-morning availability, and team-first attitude to the Cashier/Stocker role at ALDI.

% --- KEY SKILLS ---
\section*{KEY SKILLS}
% itemsep=0pt and topsep=2pt pulls the lists tighter together to save vertical space
\begin{itemize}[leftmargin=0.25in, label={$\bullet$}, itemsep=0pt, topsep=2pt]
    \item \textbf{Customer Service:} Prompt, courteous, and highly patient (experience de-escalating upset clients).
    \item \textbf{Operations \& Math:} Accurate cash handling, basic arithmetic, and quick to learn POS systems.
    \item \textbf{Physical Stamina:} Able to lift and carry up to 45 lbs, stand for long periods, and work in varying store temperatures.
    \item \textbf{Reliability:} Excellent attendance record and fully available for shifts as early as 5:00 AM.
    \item \textbf{Organization:} Strong attention to detail with experience in inventory tracking.
\end{itemize}

% --- WORK HISTORY ---
\section*{WORK HISTORY}

\noindent \textbf{Elton Jenkins Law, P.L.L.C.} \hfill \textbf{Norman, OK} \\
\textit{Technology \& Systems Lead} \hfill \textit{2017 -- Present}
\begin{itemize}[leftmargin=0.25in, label={$\bullet$}, itemsep=0pt, topsep=2pt]
    \item Set up, maintained, and troubleshot office computer hardware and equipment, ensuring everything ran smoothly and efficiently.
    \item Patiently helped staff resolve technical issues so they could get back to work quickly.
    \item Organized the firm's digital inventory and automated data entry tasks, which cut down on errors and sped up daily operations.
\end{itemize}

\vspace{4pt}

\noindent \textit{Paralegal (Concurrent Role)} \hfill \textit{2017 -- Present}
\begin{itemize}[leftmargin=0.25in, label={$\bullet$}, itemsep=0pt, topsep=2pt]
    \item Greeted and assisted a high volume of clients daily. Used empathy and clear communication to calm anxious individuals and provide great, supportive service.
    \item Carefully managed complex legal documents, demonstrating the strict attention to detail needed for tasks like accurate cash handling and basic math.
    \item Worked closely with the office team to prioritize daily tasks, adapt to sudden changes, and meet tight deadlines.
\end{itemize}

% --- EDUCATION ---
\section*{EDUCATION}

\noindent \textbf{Bachelor of Arts in Economics} \hfill \textbf{Norman, OK} \\
\textit{University of Oklahoma} 
\begin{itemize}[leftmargin=0.25in, label={$\bullet$}, itemsep=0pt, topsep=2pt]
    \item Dean's Honor Roll (4 Semesters)
    \item Study Abroad program in Hong Kong, enhancing cross-cultural communication and collaboration skills.
\end{itemize}

% --- VOLUNTEER WORK ---
\section*{VOLUNTEER WORK}

\noindent \textbf{Community Food Drive Organizer} $|$ \textit{University of Oklahoma} 
\begin{itemize}[leftmargin=0.25in, label={$\bullet$}, itemsep=0pt, topsep=2pt]
    \item Coordinated the physical loading, unloading, and distribution of goods for local families, ensuring organized inventory handling and accurate order matching.
\end{itemize}

\vspace{2pt}

\noindent \textbf{Camp Crimson Small Group Leader} $|$ \textit{University of Oklahoma} 
\begin{itemize}[leftmargin=0.25in, label={$\bullet$}, itemsep=0pt, topsep=2pt]
    \item Mentored 15+ incoming freshmen in a fast-paced environment, demonstrating strong verbal communication, leadership, and the ability to work collaboratively.
\end{itemize}

\end{document}